---
title: "plant_project_stats_figures"
output: html_document
date: "2023-10-10"
---

# Genome copy number predicts extreme evolutionary rate variation in plant mitochondrial DNA

### Getting Everything Setup, installing packages

```{r,echo=FALSE}
library(ape)
library(phangorn) #dependency for geiger
library(nlme)
library(phytools)
library(Rcpp) #dependency for geiger
library(geiger)
library(lme4)
library(ggbreak)
library(tidyverse)
library(ggpubr)
library(gridExtra)
```

### Importing datasets

This analysis needs a tree as well as the dataset. The csv file has the info for the plastid and mt copy number and rates as well as other factors. It already has Silene undulata and Aragoa abietina removed due to terminal branch divergence times of less than 1my. Pelargonium Nanum was also removed from this csv for lack of terminal branch length.

The tree is the matk tree which was run in raxml. Asscession numbers are in the supplement.

```{r}
#Read in the tree
tree<-read.nexus('matk_tree_with_groups')  # 'read.tree' also works for some formats

#Read in the dataset
dataset_dr_brnch_c_and_seq_est<-read.csv('main_data.csv')
```

#Code to drop these species from the tree.

```{r}
#Define a list of tip species to drop from the tree -- the species with NAs. Use double quotes around any names with single quotes.
#These are the species that had short branches
tips_tree_1=c("Aragoa_abietina",
              "Silene_undulata", "Pelargonium_nanum"
)

#Remove tips
tree_1<-drop.tip(phy=tree, tips_tree_1)

tree_1$edge.length<-rep(1,114)  ##IMPORTANT this line makes the tree have equal branch lengths.

#Check that tip-removal worked
plot(tree_1,cex=0.3  )
```

This generates the Brownian motion matrix using the tree.

```{r}
species = dataset_dr_brnch_c_and_seq_est$Species
bm.dataset_dr_brnch_c_and_seq_est<-corBrownian(phy=tree_1,form=~species)
```

C value data import

```{r}
####C val estimates
copy_dataset_dropped_tips_c_val<-read.csv('c_value.csv') 

#This is myddpcr data
copy_data<- read_csv("08_26_22_per_sample_copy_data_ddpcr.csv")
```

## Copy number and rate correlations

### Mito Correlations with copy number and Rate

Mito raw data, regular linear model.

```{r}
mito_lm_rate_copy <- summary(lm(mt_ds_div_mya~mito_copy,data=dataset_dr_brnch_c_and_seq_est))

mito_lm_rate_copy_t <- mito_lm_rate_copy$coefficients[2,][3]
mito_lm_rate_copy_p <- mito_lm_rate_copy$coefficients[2,][4]
```

Mito raw data, PGLS.

```{r}
mito_gls_rate_copy <- summary(gls(mt_ds_div_mya~mito_copy,data=dataset_dr_brnch_c_and_seq_est,correlation = bm.dataset_dr_brnch_c_and_seq_est)) 

mito_gls_rate_copy_t <- mito_gls_rate_copy$tTable[2,][3]
mito_gls_rate_copy_p <- mito_gls_rate_copy$tTable[2,][4]
```

Mito log10 data, regular linear model.

```{r}
mito_log_lm_rate_copy <- summary(lm(log10(mt_ds_div_mya)~log10(mito_copy),data=dataset_dr_brnch_c_and_seq_est))

mito_log_lm_rate_copy_t <- mito_log_lm_rate_copy$coefficients[2,][3]
mito_log_lm_rate_copy_p <- mito_log_lm_rate_copy$coefficients[2,][4]
```

Mito log10 data, PGLS.

```{r}
mito_log_gls_rate_copy <- summary(gls(log10(mt_ds_div_mya)~log10(mito_copy),data=dataset_dr_brnch_c_and_seq_est,correlation = bm.dataset_dr_brnch_c_and_seq_est))

mito_log_gls_rate_copy_t <- mito_log_gls_rate_copy$tTable[2,][3]
mito_log_gls_rate_copy_p <- mito_log_gls_rate_copy$tTable[2,][4]
```

### Plastid Correlations with copy number and Rate

Plastid raw data, regular linear model.

```{r}
pt_lm_rate_copy <- summary(lm(pt_ds_div_mya~plastid_copy,data=dataset_dr_brnch_c_and_seq_est)) 

pt_lm_rate_copy_t <- pt_lm_rate_copy$coefficients[2,][3]
pt_lm_rate_copy_p <- pt_lm_rate_copy$coefficients[2,][4]
```

Plastid raw data, PGLS.

```{r}
pt_gls_rate_copy <- summary(gls(pt_ds_div_mya~plastid_copy,data=dataset_dr_brnch_c_and_seq_est,correlation = bm.dataset_dr_brnch_c_and_seq_est))

pt_gls_rate_copy_t <- pt_gls_rate_copy$tTable[2,][3]
pt_gls_rate_copy_p <- pt_gls_rate_copy$tTable[2,][4]
```

Plastid log10 data, regular linear model.

```{r}
pt_log_lm_rate_copy <- summary(lm(log10(pt_ds_div_mya)~log10(plastid_copy),data=dataset_dr_brnch_c_and_seq_est))

pt_log_lm_rate_copy_t <- pt_log_lm_rate_copy$coefficients[2,][3]
pt_log_lm_rate_copy_p <- pt_log_lm_rate_copy$coefficients[2,][4]
```

Plastid log10 data, PGLS.

```{r}
pt_log_gls_rate_copy <- summary(gls(log10(pt_ds_div_mya)~log10(plastid_copy),data=dataset_dr_brnch_c_and_seq_est,correlation = bm.dataset_dr_brnch_c_and_seq_est))

pt_log_gls_rate_copy_t <- pt_log_gls_rate_copy$tTable[2,][3]
pt_log_gls_rate_copy_p <- pt_log_gls_rate_copy$tTable[2,][4]
```

## Copy number and genome size correlations

### Mito Correlations with copy number and genome size

Mito raw data, regular linear model.

```{r}
mito_lm_genome_copy <- summary(lm(mt_genome_estimate/1000~mito_copy,data=dataset_dr_brnch_c_and_seq_est))

mito_lm_genome_copy_t <- mito_lm_genome_copy$coefficients[2,][3]
mito_lm_genome_copy_p <- mito_lm_genome_copy$coefficients[2,][4]
```

Mito raw data, PGLS.

```{r}
mito_gls_genome_copy <- summary(gls(mt_genome_estimate/1000~mito_copy,data=dataset_dr_brnch_c_and_seq_est,correlation = bm.dataset_dr_brnch_c_and_seq_est)) 

mito_gls_genome_copy_t <- mito_gls_genome_copy$tTable[2,][3]
mito_gls_genome_copy_p <- mito_gls_genome_copy$tTable[2,][4]
```

Mito log10 data, regular linear model.

```{r}
mito_log_lm_genome_copy <- summary(lm(log10(mt_genome_estimate/1000)~log10(mito_copy),data=dataset_dr_brnch_c_and_seq_est))

mito_log_lm_genome_copy_t <- mito_log_lm_genome_copy$coefficients[2,][3]
mito_log_lm_genome_copy_p <- mito_log_lm_genome_copy$coefficients[2,][4]
```

Mito log10 data, PGLS.

```{r}
mito_log_gls_genome_copy <- summary(gls(log10(mt_genome_estimate/1000)~log10(mito_copy),data=dataset_dr_brnch_c_and_seq_est,correlation = bm.dataset_dr_brnch_c_and_seq_est))

mito_log_gls_genome_copy_t <- mito_log_gls_genome_copy$tTable[2,][3]
mito_log_gls_genome_copy_p <- mito_log_gls_genome_copy$tTable[2,][4]
```

### Plastid Correlations with copy number and genome size

Plastid raw data, regular linear model.

```{r}
pt_lm_genome_copy <- summary(lm(plastome_length/1000~plastid_copy,data=dataset_dr_brnch_c_and_seq_est)) 

pt_lm_genome_copy_t <- pt_lm_genome_copy$coefficients[2,][3]
pt_lm_genome_copy_p <- pt_lm_genome_copy$coefficients[2,][4]
```

Plastid raw data, PGLS.

```{r}
pt_gls_genome_copy <- summary(gls(plastome_length/1000~plastid_copy,data=dataset_dr_brnch_c_and_seq_est,correlation = bm.dataset_dr_brnch_c_and_seq_est))

pt_gls_genome_copy_t <- pt_gls_genome_copy$tTable[2,][3]
pt_gls_genome_copy_p <- pt_gls_genome_copy$tTable[2,][4]
```

Plastid log10 data, regular linear model.

```{r}
pt_log_lm_genome_copy <- summary(lm(log10(plastome_length/1000)~log10(plastid_copy),data=dataset_dr_brnch_c_and_seq_est))

pt_log_lm_genome_copy_t <- pt_log_lm_genome_copy$coefficients[2,][3]
pt_log_lm_genome_copy_p <- pt_log_lm_genome_copy$coefficients[2,][4]
```

Plastid log10 data, PGLS.

```{r}
pt_log_gls_genome_copy <- summary(gls(log10(plastome_length/1000)~log10(plastid_copy),data=dataset_dr_brnch_c_and_seq_est,correlation = bm.dataset_dr_brnch_c_and_seq_est))

pt_log_gls_genome_copy_t <- pt_log_gls_genome_copy$tTable[2,][3]
pt_log_gls_genome_copy_p <- pt_log_gls_genome_copy$tTable[2,][4]
```

## Rate and genome size correlations

### Mito Correlations with genome size and rate

Mito raw data, regular linear model.

```{r}
mito_lm_genome_rate <- summary(lm(mt_ds_div_mya~I(mt_genome_estimate/1000),data=dataset_dr_brnch_c_and_seq_est))

mito_lm_genome_rate_t <- mito_lm_genome_rate$coefficients[2,][3]
mito_lm_genome_rate_p <- mito_lm_genome_rate$coefficients[2,][4]
```

Mito raw data, PGLS.

```{r}
mito_gls_genome_rate <- summary(gls(mt_ds_div_mya~I(mt_genome_estimate/1000),data=dataset_dr_brnch_c_and_seq_est,correlation = bm.dataset_dr_brnch_c_and_seq_est)) 

mito_gls_genome_rate_t <- mito_gls_genome_rate$tTable[2,][3]
mito_gls_genome_rate_p <- mito_gls_genome_rate$tTable[2,][4]
```

Mito log10 data, regular linear model.

```{r}
mito_log_lm_genome_rate <- summary(lm(log10(mt_ds_div_mya)~log10(mt_genome_estimate/1000),data=dataset_dr_brnch_c_and_seq_est))

mito_log_lm_genome_rate_t <- mito_log_lm_genome_rate$coefficients[2,][3]
mito_log_lm_genome_rate_p <- mito_log_lm_genome_rate$coefficients[2,][4]
```

Mito log10 data, PGLS.

```{r}

mito_log_gls_genome_rate<-summary(gls(log10(mt_ds_div_mya)~log10(mt_genome_estimate/1000),data=dataset_dr_brnch_c_and_seq_est,correlation = bm.dataset_dr_brnch_c_and_seq_est))

mito_log_gls_genome_rate_t <- mito_log_gls_genome_rate$tTable[2,][3]
mito_log_gls_genome_rate_p <- mito_log_gls_genome_rate$tTable[2,][4]
```

### Plastid Correlations with genome size and rate

Plastid raw data, regular linear model.

```{r}
pt_lm_genome_rate <- summary(lm(pt_ds_div_mya~I(plastome_length/1000),data=dataset_dr_brnch_c_and_seq_est)) 

pt_lm_genome_rate_t <- pt_lm_genome_rate$coefficients[2,][3]
pt_lm_genome_rate_p <- pt_lm_genome_rate$coefficients[2,][4]
```

Plastid raw data, PGLS.

```{r}
pt_gls_genome_rate <- summary(gls(pt_ds_div_mya~I(plastome_length/1000),data=dataset_dr_brnch_c_and_seq_est,correlation = bm.dataset_dr_brnch_c_and_seq_est))

pt_gls_genome_rate_t <- pt_gls_genome_rate$tTable[2,][3]
pt_gls_genome_rate_p <- pt_gls_genome_rate$tTable[2,][4]
```

Plastid log10 data, regular linear model.

```{r}
pt_log_lm_genome_rate <- summary(lm(log10(pt_ds_div_mya)~log10(plastome_length/1000),data=dataset_dr_brnch_c_and_seq_est))

pt_log_lm_genome_rate_t <- pt_log_lm_genome_rate$coefficients[2,][3]
pt_log_lm_genome_rate_p <- pt_log_lm_genome_rate$coefficients[2,][4]
```

Plastid log10 data, PGLS.

```{r}
pt_log_gls_genome_rate <- summary(gls(log10(pt_ds_div_mya)~log10(plastome_length/1000),data=dataset_dr_brnch_c_and_seq_est,correlation = bm.dataset_dr_brnch_c_and_seq_est))

pt_log_gls_genome_rate_t <- pt_log_gls_genome_rate$tTable[2,][3]
pt_log_gls_genome_rate_p <- pt_log_gls_genome_rate$tTable[2,][4]
```

```{r}
p_t_values <- tibble(analysis= character(),t = numeric(),p = numeric())

p_t_values <- p_t_values %>% 
  add_row(analysis="mito_lm_rate_copy",p=mito_lm_rate_copy_p,t=mito_lm_rate_copy_t) %>%
  add_row(analysis="mito_gls_rate_copy",p=mito_gls_rate_copy_p,t=mito_gls_rate_copy_t) %>%
  add_row(analysis="mito_log_lm_rate_copy",p=mito_log_lm_rate_copy_p,t=mito_log_lm_rate_copy_t) %>%
  add_row(analysis="mito_log_gls_rate_copy",p=mito_log_gls_rate_copy_p,t=mito_log_gls_rate_copy_t) %>%
  
  add_row(analysis="pt_lm_rate_copy",p=pt_lm_rate_copy_p,t=pt_lm_rate_copy_t) %>%
  add_row(analysis="pt_gls_rate_copy",p=pt_gls_rate_copy_p,t=pt_gls_rate_copy_t) %>%
  add_row(analysis="pt_log_lm_rate_copy",p=pt_log_lm_rate_copy_p,t=pt_log_lm_rate_copy_t) %>%
  add_row(analysis="pt_log_gls_rate_copy",p=pt_log_gls_rate_copy_p,t=pt_log_gls_rate_copy_t) %>%
  
  add_row(analysis="mito_lm_genome_copy",p=mito_lm_genome_copy_p,t=mito_lm_genome_copy_t) %>%
  add_row(analysis="mito_gls_genome_copy",p=mito_gls_genome_copy_p,t=mito_gls_genome_copy_t) %>%
  add_row(analysis="mito_log_lm_genome_copy",p=mito_log_lm_genome_copy_p,t=mito_log_lm_genome_copy_t) %>%
  add_row(analysis="mito_log_gls_genome_copy",p=mito_log_gls_genome_copy_p,t=mito_log_gls_genome_copy_t) %>%
  
  add_row(analysis="pt_lm_genome_copy",p=pt_lm_genome_copy_p,t=pt_lm_genome_copy_t) %>%
  add_row(analysis="pt_gls_genome_copy",p=pt_gls_genome_copy_p,t=pt_gls_genome_copy_t) %>%
  add_row(analysis="pt_log_lm_genome_copy",p=pt_log_lm_genome_copy_p,t=pt_log_lm_genome_copy_t) %>%
  add_row(analysis="pt_log_gls_genome_copy",p=pt_log_gls_genome_copy_p,t=pt_log_gls_genome_copy_t) %>%

  add_row(analysis="mito_lm_genome_rate",p=mito_lm_genome_rate_p,t=mito_lm_genome_rate_t) %>%
  add_row(analysis="mito_gls_genome_rate",p=mito_gls_genome_rate_p,t=mito_gls_genome_rate_t) %>%
  add_row(analysis="mito_log_lm_genome_rate",p=mito_log_lm_genome_rate_p,t=mito_log_lm_genome_rate_t) %>%
  add_row(analysis="mito_log_gls_genome_rate",p=mito_log_gls_genome_rate_p,t=mito_log_gls_genome_rate_t) %>%
  
  add_row(analysis="pt_lm_genome_rate",p=pt_lm_genome_rate_p,t=pt_lm_genome_rate_t) %>%
  add_row(analysis="pt_gls_genome_rate",p=pt_gls_genome_rate_p,t=pt_gls_genome_rate_t) %>%
  add_row(analysis="pt_log_lm_genome_rate",p=pt_log_lm_genome_rate_p,t=pt_log_lm_genome_rate_t) %>%
  add_row(analysis="pt_log_gls_genome_rate",p=pt_log_gls_genome_rate_p,t=pt_log_gls_genome_rate_t) 
 
p_t_values %>% print(n=40)
```

#Dn analysis

```{r}
#Define a list of tip species to drop from the tree -- the species with NAs. Use double quotes around any names with single quotes.
#These are the species that had short branches
tips_tree_2=c('Pelargonium_australe',
              'Pelargonium_exstipulatum',
              'Plantago_rugelii',
              'Silene_noctiflora'
)

#Remove tips
tree_2<-drop.tip(phy=tree_1, tips_tree_2)

#filters out plastid data with zero for dn
plastid_dn_dataset <-filter(dataset_dr_brnch_c_and_seq_est, pt_dn!=0)

#sets species data for new dataset for bm
species_dn = plastid_dn_dataset$Species

#creates new bm data for plastid gls
bm.dataset_dr_brnch_c_and_seq_est_dn<-corBrownian(phy=tree_2,form=~species_dn)

#Models for mito dn change and copy num
mito_log_lm_dn_copy <- summary(lm(log10(mito_dn/time..mya.)~log10(mito_copy),data=dataset_dr_brnch_c_and_seq_est)) #regular lm
mito_log_lm_dn_copy_t <- mito_log_lm_dn_copy$coefficients[2,][3] #t
mito_log_lm_dn_copy_p <- mito_log_lm_dn_copy$coefficients[2,][4] #p

mito_log_gls_dn_copy <- summary(gls(log10(mito_dn/time..mya.)~log10(mito_copy),data=dataset_dr_brnch_c_and_seq_est,correlation = bm.dataset_dr_brnch_c_and_seq_est))$tTable #gls
mito_log_gls_dn_copy_t <- mito_log_gls_dn_copy[2,][3] #t
mito_log_gls_dn_copy_p <- mito_log_gls_dn_copy[2,][4] #p

#Models for pt dn change and copy num
pt_log_lm_dn_copy<- summary(lm(log10(pt_dn/time..mya.)~log10(plastid_copy),data=plastid_dn_dataset)) #regular lm
pt_log_lm_dn_copy_t <- pt_log_lm_dn_copy$coefficients[2,][3] #t
pt_log_lm_dn_copy_p <- pt_log_lm_dn_copy$coefficients[2,][4] #p

pt_log_gls_dn_copy <- summary(gls(log10(pt_dn/time..mya.)~log10(plastid_copy),data=plastid_dn_dataset,correlation = bm.dataset_dr_brnch_c_and_seq_est_dn))$tTable #gls
pt_log_gls_dn_copy_t <- pt_log_gls_dn_copy[2,][3] #t
pt_log_gls_dn_copy_p <- pt_log_gls_dn_copy[2,][4] #p

#Models for mito dn change and genome estimate
mito_log_lm_dn_genome<-summary(lm(log10(mito_dn/time..mya.)~log10(mt_genome_estimate/1000),data=dataset_dr_brnch_c_and_seq_est)) #regular lm
mito_log_lm_dn_genome_t <- mito_log_lm_dn_genome$coefficients[2,][3] #t
mito_log_lm_dn_genome_p <- mito_log_lm_dn_genome$coefficients[2,][4] #p

mito_log_gls_dn_genome<-summary(gls(log10(mito_dn/time..mya.)~log10(mt_genome_estimate/1000),data=dataset_dr_brnch_c_and_seq_est,correlation = bm.dataset_dr_brnch_c_and_seq_est))$tTable #gls
mito_log_gls_dn_genome_t <- mito_log_gls_dn_genome[2,][3] #t
mito_log_gls_dn_genome_p <- mito_log_gls_dn_genome[2,][4] #p

#Models for pt dn change and plastome length
pt_log_lm_dn_genome <- summary(lm(log10(pt_dn/time..mya.)~log10(plastome_length/1000),data=plastid_dn_dataset)) #regular lm
pt_log_lm_dn_genome_t <- pt_log_lm_dn_genome$coefficients[2,][3] #t
pt_log_lm_dn_genome_p <- pt_log_lm_dn_genome$coefficients[2,][4] #p

pt_log_gls_dn_genome <- summary(gls(log10(pt_dn/time..mya.)~log10(plastome_length/1000),data=plastid_dn_dataset,correlation = bm.dataset_dr_brnch_c_and_seq_est_dn))$tTable #gls
pt_log_gls_dn_genome_t <- pt_log_gls_dn_genome[2,][3] #t
pt_log_gls_dn_genome_p <- pt_log_gls_dn_genome[2,][4] #p

```


#dn/ds analysis

```{r}
mt_log_lm_dn_ds_copy <- summary(lm(log10(mito_dn/mt_ds)~log10(mito_copy),data=dataset_dr_brnch_c_and_seq_est)) #regular lm
mt_log_lm_dn_ds_copy_t <- mt_log_lm_dn_ds_copy$coefficients[2,][3] #t
mt_log_lm_dn_ds_copy_p <- mt_log_lm_dn_ds_copy$coefficients[2,][4] #p
mt_log_lm_dn_ds_copy

mt_log_gls_dn_ds_copy <- summary(gls(log10(mito_dn/mt_ds)~log10(mito_copy),data=dataset_dr_brnch_c_and_seq_est,correlation = bm.dataset_dr_brnch_c_and_seq_est))$tTable #gls
mt_log_gls_dn_ds_copy_t <- mt_log_gls_dn_ds_copy[2,][3] #t
mt_log_gls_dn_ds_copy_p <- mt_log_gls_dn_ds_copy[2,][4] #p
mt_log_gls_dn_ds_copy


#Models for pt dn change and plastome length
pt_log_lm_dn_ds_copy <- summary(lm(log10(pt_dn/pt_ds)~log10(plastid_copy),data=plastid_dn_dataset)) #regular lm
pt_log_lm_dn_ds_copy_t <- pt_log_lm_dn_ds_copy$coefficients[2,][3] #t
pt_log_lm_dn_ds_copy_p <- pt_log_lm_dn_ds_copy$coefficients[2,][4] #p
pt_log_lm_dn_ds_copy

pt_log_gls_dn_ds_copy <- summary(gls(log10(pt_dn/pt_ds)~log10(plastid_copy),data=plastid_dn_dataset,correlation = bm.dataset_dr_brnch_c_and_seq_est_dn))$tTable #gls
pt_log_gls_dn_ds_copy_t <- pt_log_gls_dn_ds_copy[2,][3] #t
pt_log_gls_dn_ds_copy_p <- pt_log_gls_dn_ds_copy[2,][4] #p
pt_log_gls_dn_ds_copy

mt_log_lm_dn_ds_genome <- summary(lm(log10(mito_dn/mt_ds)~log10(mt_genome_estimate/1000),data=dataset_dr_brnch_c_and_seq_est)) #regular lm
mt_log_lm_dn_ds_genome_t <- mt_log_lm_dn_ds_copy$coefficients[2,][3] #t
mt_log_lm_dn_ds_genome_p <- mt_log_lm_dn_ds_copy$coefficients[2,][4] #p

mt_log_gls_dn_ds_genome <- summary(gls(log10(mito_dn/mt_ds)~log10(mt_genome_estimate/1000),data=dataset_dr_brnch_c_and_seq_est,correlation = bm.dataset_dr_brnch_c_and_seq_est))$tTable #gls
mt_log_gls_dn_ds_genome_t <- mt_log_gls_dn_ds_genome[2,][3] #t
mt_log_gls_dn_ds_genome_p <- mt_log_gls_dn_ds_genome[2,][4] #p

#Models for pt dn change and plastome length
pt_log_lm_dn_ds_genome <- summary(lm(log10(pt_dn/pt_ds)~log10(plastome_length/1000),data=plastid_dn_dataset)) #regular lm
pt_log_lm_dn_ds_genome_t <- pt_log_lm_dn_ds_genome$coefficients[2,][3] #t
pt_log_lm_dn_ds_genome_p <- pt_log_lm_dn_ds_genome$coefficients[2,][4] #p

pt_log_gls_dn_ds_genome <- summary(gls(log10(pt_dn/pt_ds)~log10(plastome_length/1000),data=plastid_dn_dataset,correlation = bm.dataset_dr_brnch_c_and_seq_est_dn))$tTable #gls
pt_log_gls_dn_ds_genome_t <- pt_log_gls_dn_ds_genome[2,][3] #t
pt_log_gls_dn_ds_genome_p <- pt_log_gls_dn_ds_genome[2,][4] #p
```


C value and ddpcr correlations

```{r}
c_value_dataset_angiosperms = filter(copy_dataset_dropped_tips_c_val,Group!="Gymnosperms")

summary(lm(log10(mito_copy_c)~0+log10(mito_copy), data=c_value_dataset_angiosperms))

plot(log10(mito_copy_c)~0+log10(mito_copy),data=c_value_dataset_angiosperms)

plot(mito_copy_c~mito_copy,data=c_value_dataset_angiosperms)

summary(lm(log10(plastid_copy_c)~0+log10(plastid_copy),data=c_value_dataset_angiosperms))

summary(lm(log10(ddpcr_mito)~0+log10(mito_copy_seq), data=copy_data))

summary(lm(log10(ddpcr_plastid)~0+log10(plastid_copy_seq), data=copy_data))

summary(lm(log10(ddpcr_mito)~log10(mito_copy_seq), data=copy_data))

summary(lm(log10(ddpcr_plastid)~log10(plastid_copy_seq), data=copy_data))

```

```{r}
summary(lm(formula = log(plastid_copy_c) ~ log(plastid_copy), data = c_value_dataset_angiosperms))
```

## Within Group Stats
```{r}

Sileneae <- dataset_dr_brnch_c_and_seq_est %>% filter(Group=="Sileneae")
Plantagineae <- dataset_dr_brnch_c_and_seq_est %>% filter(Group=="Plantagineae")
Geraniales <- dataset_dr_brnch_c_and_seq_est %>% filter(Group=="Geraniales")
Gymnosperms <- dataset_dr_brnch_c_and_seq_est %>% filter(Group=="Gymnosperms")

summary(lm(log10(mt_ds_div_mya)~log10(mito_copy),data=Sileneae))
summary(lm(log10(mt_ds_div_mya)~log10(mito_copy),data=Plantagineae))
summary(lm(log10(mt_ds_div_mya)~log10(mito_copy),data=Geraniales))
summary(lm(log10(mt_ds_div_mya)~log10(mito_copy),data=Gymnosperms))

summary(lm(log10(pt_ds_div_mya)~log10(plastid_copy),data=Sileneae))
summary(lm(log10(pt_ds_div_mya)~log10(plastid_copy),data=Plantagineae))
summary(lm(log10(pt_ds_div_mya)~log10(plastid_copy),data=Geraniales))
summary(lm(log10(pt_ds_div_mya)~log10(plastid_copy),data=Gymnosperms))


summary(lm(log10(mt_genome_estimate)~log10(mito_copy),data=Sileneae))
summary(lm(log10(mt_genome_estimate)~log10(mito_copy),data=Plantagineae))
summary(lm(log10(mt_genome_estimate)~log10(mito_copy),data=Geraniales))
summary(lm(log10(mt_genome_estimate)~log10(mito_copy),data=Gymnosperms))

summary(lm(log10(plastome_length)~log10(plastid_copy),data=Sileneae))
summary(lm(log10(plastome_length)~log10(plastid_copy),data=Plantagineae))
summary(lm(log10(plastome_length)~log10(plastid_copy),data=Geraniales))
summary(lm(log10(plastome_length)~log10(plastid_copy),data=Gymnosperms))
```

##wilcox test
```{r}
angiosperms <- filter(copy_dataset_dropped_tips_c_val, Group!="Gymnosperms")

gymnosperms <- filter(copy_dataset_dropped_tips_c_val, Group=="Gymnosperms")

wilcox.test(angiosperms$pt_ds_div_mya, gymnosperms$pt_ds_div_mya)
```

##Copy number statistics for c value

```{r}
##This repeats analysis for c value
#Define a list of tip species to drop from the tree -- the species with NAs. Use double quotes around any names with single quotes.
#These are the species that had short branches
tips_tree_2=c('Abies_sibirica',
'Agrostemma_githago',
'Arabidopsis_thaliana',
'Ceratozamia_hildae',
'Cupressus_sempervirens',
'Erodium_chrysanthum',
'Erodium_gruinum',
'Erodium_moschatum',
'Erodium_texanum',
'Erodium_trifolium',
'Geranium_brycei',
'Geranium_incanum',
'Geranium_maderense',
'Geranium_phaeum',
'Geranium_sanguineum',
'Ginkgo_biloba',
'Gnetum_gnemon',
'Hesperocyparis_glabra',
'Melianthus_villosus',
'Nicotiana_tabacum',
'Pelargonium_australe',
'Pelargonium_citronellum',
'Pelargonium_cotyledonis',
'Pelargonium_exstipulatum',
'Pelargonium_fulgidum',
'Pelargonium_hortorum',
'Pelargonium_myrrhifolium',
'Pelargonium_tetragonum',
'Pelargonium_transvaalense',
'Picea_abies',
'Plantago_arenaria',
'Plantago_aristata',
'Plantago_coronopus',
'Plantago_crassifolia',
'Plantago_depressa',
'Plantago_elongata',
'Plantago_maritima',
'Plantago_media',
'Plantago_rigida',
'Plantago_rugelii',
'Plantago_sericea',
'Plantago_tenuiflora',
'Podocarpus_macrophyllus',
'Silene_conica',
'Silene_latifolia',
'Silene_noctiflora',
'Silene_vulgaris',
'Taxus_baccata',
'Welwitschia_mirabilis',
'Zamia_integrifolia',
'Zea_mays'
)

#Remove tips
tree_2<-keep.tip(phy=tree, tips_tree_2)

tree_2$edge.length<-rep(1,114)  ##IMPORTANT this line makes the tree have equal branch lengths.


#Check that tip-removal worked
plot(tree_2,cex=0.3  )

species2 = copy_dataset_dropped_tips_c_val$Species
bm.dataset_dr_brnch_c_est<-corBrownian(phy=tree_2,form=~species2)

bm.dataset_dr_brnch_c_est
copy_dataset_dropped_tips_c_val



summary(lm(log10(mt_ds_div_mya)~log10(mito_copy_c),data=copy_dataset_dropped_tips_c_val))

summary(gls(log10(mt_ds_div_mya)~log10(mito_copy_c),data=copy_dataset_dropped_tips_c_val,correlation = bm.dataset_dr_brnch_c_est))$tTable

summary(lm(log10(pt_ds_div_mya)~log10(plastid_copy_c),data=copy_dataset_dropped_tips_c_val))

summary(gls(log10(pt_ds_div_mya)~log10(plastid_copy_c),data=copy_dataset_dropped_tips_c_val,correlation = bm.dataset_dr_brnch_c_est))$tTable

summary(lm(log10(mito_copy)~log10(mito_copy_c), c_value_dataset_angiosperms))

summary(lm(log10(plastid_copy)~log10(plastid_copy_c), c_value_dataset_angiosperms))



summary(lm(log10(mt_genome_estimate)~log10(mito_copy_c),data=copy_dataset_dropped_tips_c_val))

summary(gls(log10(mt_genome_estimate)~log10(mito_copy_c),data=copy_dataset_dropped_tips_c_val,correlation = bm.dataset_dr_brnch_c_est))$tTable

summary(lm(log10(plastome_length)~log10(plastid_copy_c),data=copy_dataset_dropped_tips_c_val))

summary(gls(log10(plastome_length)~log10(plastid_copy_c),data=copy_dataset_dropped_tips_c_val,correlation = bm.dataset_dr_brnch_c_est))$tTable


summary(lm(plastid_copy_seq~ddpcr_plastid,data=copy_data))

summary(lm(mito_copy_seq~ddpcr_mito,data=copy_data))
```


